---
title: "Flex Dsashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

Here I use the `Instacart` dataset, and load it from the p8105.datasets package. The `instacart` dataset is large, thus here I only used the `product_name == "Spring Water"` and `add_to_cart_order >= 15` data (127 obs) to ensure a reasonable product. Using the filtered `Instacart` dataset, we can check the big customers' (purchase >= 15 in an order) behavior in purchasing Spring Water. 3 plots provided.

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

library(flexdashboard)
library(plotly)

data(instacart)
instacart = 
  instacart %>% 
  filter(
    product_name == "Spring Water",
    add_to_cart_order >= 15,
    !is.na(reordered),
    !is.na(days_since_prior_order)
    ) %>% 
  mutate(
    user_id = as.character(user_id),
    reordered2 = ifelse(reordered == 0, "new customer", "reordered customer")
    )
```

-----------------------------------------------------------------------

### Chart A: Figure out those "Big customers" for Spring Water


Let's figure out those users who would like to buy a lot of Spring Waters (>= 15 in an order), and see who would love to reorder among these "big customers"!


```{r}
instacart %>%
  mutate(user_id = fct_reorder(user_id, add_to_cart_order)) %>% 
  plot_ly(
  x = ~user_id, y = ~add_to_cart_order, color = ~reordered2, 
  type = "bar", colors = "viridis", width = 900
  )
```


Here we can see the User ID of those purchase >= 15 Spring Water in an order. About half of them are reordered costumers - the Spring Water vendor should pay closer attention to those reordered big customers.


-----------------------------------------------------------------------


### Chart B: The time of purchasing Spring Water


Let's figure out the time trend in a day when the "big customers" like to buy Spring Waters, and see if there's difference in the time pattern between those reordered & new customers!


```{r}
instacart %>% 
  mutate(order_hour_of_day = sort(order_hour_of_day)
         ) %>% 
  plot_ly(x = ~order_hour_of_day, y = ~add_to_cart_order, color = ~reordered2, 
          type = "box", colors = "viridis", width = 900)
```


Here we can see that most big customers purchase Spring Water between 7am and 22pm. 

More reordered big customers tend to purchase in the morning, while more new big customers tend to purchase in the afternoon. This could provide some insights for the supermarket supply chain to pick a time of importing Spring Water.


-----------------------------------------------------------------------


### Chart C: Figure out the pattern between frequency of purchase and number of purchase


Let's figure out the pattern between frequency of purchase and number of purchase, among the big customers of Spring Water.


```{r}
instacart %>% 
  plot_ly(
      x = ~days_since_prior_order, y = ~add_to_cart_order, color = ~reordered2,
      type = "scatter", mode = "markers" , width = 900)
```


Here we can see that among the big customers of Spring Water, 4-10 days or 30 days since prior order would be a most frequent time period for reorder. The new customers' days since prior order spread evenly from 5-30 days. 

